En garde! Unguarded iteration for reversible computation in the Delay monad\thanks{Niccol\`o Veltri was supported by a research grant (13156) from VILLUM FONDEN.}

### 2019-04-29 mpc19/paper.tex
my acknowledgements

\begin{document}
%
\title{En garde! Unguarded iteration for reversible computation in the Delay monad\thanks{Supported by organization x.}}
%
\titlerunning{Unguarded iteration for reversible computation in the Delay monad}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robin Kaarsgaard \inst{1}\orcidID{0000-0002-7672-799X} \and
Niccol\`o Veltri\inst{2}\orcidID{0000-0002-7230-3436}}
%
\authorrunning{Kaarsgaard and Veltri}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIKU, Department of Computer Science, University of
    Copenhagen\\ \email{robin@di.ku.dk} \and
Department of Computer Science, IT University of
    Copenhagen\\ \email{nive@itu.dk}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Reversible computation studies computations which exhibit both forward and
backward determinism. Among others, it has been studied for half a century for
its applications in low-power computing, and forms the basis for quantum
computing.

@@

We conclude this section by remarking that the construction of a trace
operator in the Kleisli category of the maybe monad is impossible
without the assumption of additional classical principles. In fact,
given a map $f : A + C \to B + C + 1$, let $xs$ be the possibly
infinite sequence of elements of $B + C + 1$ produced by the iteration
of $f$ on a given input $A + C$. In order to construct the trace of
$f$, we need to decide whether $xs$ is a finite sequence terminating
with an element of $B + 1$, or $xs$ is an infinite stream of elements
of $C$. This decision requires the limited principle of omniscience,
an instance of the law of excluded middle not provable in Martin-L\"of
type theory.
\[
\mathsf{LPO} = (s : \mathbb{N} \to 2) \to ((n : \mathbb{N}) \times
s\,n \equiv \mathsf{true}) + ((n : \mathbb{N}) \to s\,n \equiv \mathsf{false})
\]

>>>>

\begin{document}
%
\title{En garde! Unguarded iteration for reversible computation in the
  Delay monad\thanks{Niccol\`o Veltri was supported by a research
    grant (13156) from VILLUM FONDEN.}}
%
\titlerunning{Unguarded iteration for reversible computation in the Delay monad}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robin Kaarsgaard \inst{1}\orcidID{0000-0002-7672-799X} \and
Niccol\`o Veltri\inst{2}\orcidID{0000-0002-7230-3436}}
%
\authorrunning{Kaarsgaard and Veltri}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIKU, Department of Computer Science, University of
    Copenhagen\\ \email{robin@di.ku.dk} \and
Department of Computer Science, IT University of
    Copenhagen\\ \email{nive@itu.dk}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Reversible computation studies computations which exhibit both forward and
backward determinism. Among others, it has been studied for half a century for
its applications in low-power computing, and forms the basis for quantum
computing.

@@

We conclude this section by remarking that the construction of a trace
operator in the Kleisli category of the maybe monad is impossible
without the assumption of additional classical principles. In fact,
given a map $f : A + C \to B + C + 1$, let $xs$ be the possibly
infinite sequence of elements of $B + C + 1$ produced by the iteration
of $f$ on a given input $A + C$. In order to construct the trace of
$f$, we need to decide whether $xs$ is a finite sequence terminating
with an element of $B + 1$, or $xs$ is an infinite stream of elements
of $C$. This decision requires the limited principle of omniscience,
an instance of the law of excluded middle not provable in Martin-L\"of
type theory:
\[
\mathsf{LPO} = (s : \mathbb{N} \to 2) \to ((n : \mathbb{N}) \times
s\,n \equiv \mathsf{true}) + ((n : \mathbb{N}) \to s\,n \equiv \mathsf{false})
\]
where $2$ is the type of booleans, with $\mathsf{true}$ and
$\mathsf{false}$ as only inhabitants.
